Dependent Object Types

### 2012-08-29 doc/candidacy/report.tex
minor

Their calculus is grounded in type theory. It is based on Girard's
$F_\omega$~\cite{tapl}. They add {\it translucent sums} to model
modules, dependent functions to model functors, a notion of subtyping
to model module implementation-interface matching. The crucial
addition and novelty is that of a {\it translucent sum}. A translucent
sum has the form of a possibly empty sequence of bindings. Similarly,
a translucent sum type has the form of a possibly empty sequence of
declarations. They differ from traditional records, because they can
contain types and because later fields can depend on ealier
ones. Translucent sums are ordinary values. Since they model modules,
it means that modules are first-class values.

@@

>>>>

Their calculus is grounded in type theory. It is based on Girard's
$F_\omega$~\cite{tapl}. They add {\it translucent sums} to model
modules, dependent functions to model functors, a notion of subtyping
to model module implementation-interface matching. The crucial
addition and novelty is that of a {\it translucent sum}. A translucent
sum has the form of a possibly empty sequence of bindings. Similarly,
a translucent sum type has the form of a possibly empty sequence of
declarations. They differ from traditional records, because they can
contain types and because later fields can depend on ealier
ones. Translucent sums are ordinary values. Since they model modules,
it means that modules are first-class values, and their module system
is higher-order ``for free''.

@@

In terms of theoretical results, there's a sketch of soundness in the
paper, but it's unclear whether it is correct. Decidability and
completeness of subtyping has not yet been established.
